Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-21 IJCAR2020/forces_definition.tex
Párrafo pelotudo sobre recursión.

\begin{framed}
  In order to prove absoluteness of functions defined by wellfounded
  recursion, we need to show that we can replace the relevant
  wellfounded relations by their transitive closures. (EXPAND HERE OR
  SOMEWHERE ELSE).
\end{framed}

>>>>

\paragraph*{Technical details}
Paulson proved absoluteness of functions defined by wellfounded
recursion over a transitive relation. Some of our definitions by
recursion (\emph{check} and \emph{forces}) do not fit in that scheme.
One can replace the relation $R$ for its transitive closure $R^+$ in the
recursive definition because one can prove, in general, that
$F\!\upharpoonright\!(R^{-1}(x))(y) =
F\!\upharpoonright\!({R^+}^{-1}(x))(y)$ whenever $(x,y) \in R$.

\begin{framed}
  TODO: ¿Qué más decimos?

  TODO: por qué no tenemos ese resultado general que mencionamos?
\end{framed}
